SubsidyExplorer - Step 0: Data Wrangling

### 2020-03-24 scripts/01_data_wrangling.Rmd
cleaning up

>>>>

# Section 5 - Relative Metrics

This second is a bit of a relic from when we were doing "country profiles", but there are a couple of relative metrics we want to calculate from our data sources. This is done here.

```{r}
# GDP
gdp_dat_mry <- wb_dat_edit %>%
  dplyr::filter(variable == "gdp") %>%
  group_by(iso3, variable) %>%
  dplyr::filter(year == max(year[!is.na(value)])) %>%
  ungroup() %>%
  dplyr::select(-units) %>%
  dplyr::select(iso3, gdp_year = year, gdp = value)

# Population
pop_dat_mry <- wb_dat_edit %>%
  dplyr::filter(variable == "population") %>%
  group_by(iso3, variable) %>%
  dplyr::filter(year == max(year[!is.na(value)])) %>%
  ungroup() %>%
  dplyr::select(-units) %>%
  dplyr::select(iso3, population_year = year, population = value)

# Fishers
fisher_dat_mry <- fao_fishers_dat_edit %>%
  group_by(iso3, variable) %>%
  dplyr::filter(year == max(year[!is.na(value)])) %>%
  ungroup() %>%
  dplyr::select(-units) %>%
  dplyr::select(iso3, fishers_year = year, fishers = value)

# FTE
fte_dat_mry <- teh_fte_dat_edit %>%
  dplyr::select(iso3, fte_year = year, fte = value)

# Capture Production

# Landed Value

# Combine with subsidy data and calculate relative metrics
relative_dat <- sumaila_2019_dat_edit %>%
  dplyr::select(-data_type, -units, -source, -variable) %>%
  rename(subs = value) %>%
  left_join()
```
